{\helveticaitalic{Supplementary Material}}

### 2022-05-03 tex/sections/results.tex
Add small edits

\subsection{Stable solution branch borders}
~\label{sec:borders}
Let $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ denote the left and right parameter borders on $\bar g$ where stable $n:n$ solutions exist.
That is, as $\bar g$ is increased stable $n:n$ solutions are created at $\bar g_{\mathcal{L}}(n)$ and destroyed at $\bar g_{\mathcal{R}}(n)$.
When $\bar g$ is reduced beyond $\bar g_{\mathcal{L}}(n)$, $n:n$ solutions bifurcate into $(n-1):(n-1)$ solutions, while when $\bar g$ is increased beyond $\bar g_{\mathcal{R}}(n)$, $n:n$ solutions bifurcate into $(n+1):(n+1)$ solutions.
Let us briefly recap our observations regarding $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
For $n>1$ there are the following relations:
\begin{align}
	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n)\label{eq:easy1},                                                                 \\
	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n+1)\text{ and } \bar g_{\mathcal{R}}(n)<\bar g_{\mathcal{L}}(n+1)\label{eq:easy2}, \\
	\bar g_{\mathcal{R}}(n+1)                             & < \bar g_{\mathcal{R}}(n)\label{eq:coexistence},                                                           \\
	\bar g_{\mathcal{L}}(n+1) - \bar g_{\mathcal{R}}(n+1) & < \bar g_{\mathcal{R}}(n) - \bar g_{\mathcal{R}}(n)\label{eq:robustness}.
\end{align}
\Cref{eq:easy1,eq:easy2} are self-explanatory.
\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n:n$ and $(n+1):(n+1)$ solutions.
\Cref{eq:robustness} implies that the parameter interval on $\bar g$ of $n:n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
\linelabel{line:branchA}
All of the above relations are reminiscent of the bifurcation scenario of type period increment with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
	see][]{gardini2012,tramontana2012,avrutin2011}.
While our maps $\Pi_n$ are fully continuous, the above observation suggests that a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
We will explore what such a map might look like in the discussion.

>>>>

\subsection{Stable solution branch borders}
~\label{sec:borders}
Let $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ denote the left and right parameter borders on $\bar g$ where stable $n:n$ solutions exist.
That is, as $\bar g$ is increased stable $n:n$ solutions are created at $\bar g_{\mathcal{L}}(n)$ and destroyed at $\bar g_{\mathcal{R}}(n)$.
When $\bar g$ is reduced beyond $\bar g_{\mathcal{L}}(n)$, $n:n$ solutions bifurcate into $(n-1):(n-1)$ solutions, while when $\bar g$ is increased beyond $\bar g_{\mathcal{R}}(n)$, $n:n$ solutions bifurcate into $(n+1):(n+1)$ solutions.
Let us briefly recap our observations regarding $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
For $n>1$ there are the following relations:
\begin{align}
	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n)\label{eq:easy1},                                                                 \\
	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n+1)\text{ and } \bar g_{\mathcal{R}}(n)<\bar g_{\mathcal{L}}(n+1)\label{eq:easy2}, \\
	\bar g_{\mathcal{R}}(n+1)                             & < \bar g_{\mathcal{R}}(n)\label{eq:coexistence},                                                           \\
	\bar g_{\mathcal{L}}(n+1) - \bar g_{\mathcal{R}}(n+1) & < \bar g_{\mathcal{R}}(n) - \bar g_{\mathcal{R}}(n)\label{eq:robustness}.
\end{align}
\Cref{eq:easy1,eq:easy2} are self-explanatory.
\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n:n$ and $(n+1):(n+1)$ solutions.
\Cref{eq:robustness} implies that the parameter interval on $\bar g$ of $n:n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
\linelabel{line:branchA}
All of the above relations are reminiscent of the bifurcation scenario of type period increment with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
	see][]{gardini2012,tramontana2012,avrutin2011}.
While our maps $\Pi_n$ are fully continuous, the above observation suggests that a different piecewise-linear scalar map that captures such period increment dynamics of the full system might exist.
We will explore what such a map might look like in the discussion.
